% LaTeX file for resume
% This file uses the resume document class (res.cls)

\documentclass{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
\usepackage{newcent}   % uses new century schoolbook postscript font
\newsectionwidth{0pt}  % So the text is not indented under section headings
\usepackage{fancyhdr}  % use this package to get a 2 line header
\usepackage[margin=0.5in]{geometry}
\renewcommand{\headrulewidth}{0pt} % suppress line drawn by default by fancyhdr
\setlength{\headheight}{24pt} % allow room for 2-line header
\setlength{\headsep}{24pt}  % space between header and text
\setlength{\headheight}{24pt} % allow room for 2-line header
\pagestyle{fancy}     % set pagestyle for document
\cfoot{}                                     % the foot is empty
\topmargin=-0.5in % start text higher on the page

\begin{document}

\begin{resume}
{\centering
{\Large \bf Jordan McConnell} \\
1360 NW Van Buren Ave \\
Corvallis, OR 97330 \\
(503) 347-9899 \\
jordanmcconnell@comcast.net
\par
}
\begin{center}
\line(1,0){450}
\end{center}

\section{OBJECTIVE}
\vspace{8pt} % provide vertical space between section title and contents
To obtain a position that is actively involved in new and emerging technologies.
\vspace{0.2in}
\section{SKILLS}
\vspace{8pt}
Proficiency: C\#, HTML/CSS, Javascript/JSON, JQuery, SQL, ASP.NET
\\
\\
Familiarity: Java, C/C++, PHP, Python
\\
\\
Software: Visual Studio 2010/2012, TFS, GIT, SVN, Vim, IIS

\vspace{0.2in}
\section{EDUCATION}
\vspace{8pt}
{\sl BS}, Computer Science, Computer Systems option \hfill Exp. Graduation July 2013\\
Oregon State University, Corvallis, OR \hfill GPA 3.16 \\

{\sl Senior Project}\\
Creating a web application for Solar World to improve the efficiency of their manufacturing process through data analysis of system alarms.
    \begin{itemize} \itemsep -1pt
    \item Gathered requirements from client by meeting with them to understanding their software needs.
    \item Queried alarm data from client's database using T-SQL with user-selected parameters.
    \item Organized data from database into a formatted table for graphing using C\#.
    \item Developed web graphing application using ASP.NET to display the data.
    \item Integrated new web application into existing website while maintaining company style.
    \end{itemize}

\vspace{0.2in}
\section{PROFESSIONAL EXPERIENCE}
\vspace{8pt}
{\sl Business Solutions Group} \hfill        February 2012 - present \\
Student Developer, Corvallis, OR

   \begin{itemize} \itemsep -1pt % reduce space between items
   \item Produced proof of concept for a mobile application for Oregon Department of Transportation using Sencha Touch and JSON that would provide hands-free text-to-speech updates of traffic.
   \item Implemented a statewide notification system for Oregon Department of Transportation using C\# and T-SQL that allows a user to notify others using a variety of communication methods
   \item Updated existing web application for Oregon State University by adding in more functionality and fixing existing bugs using C\#, ASP.NET, and JQuery.
   \item Created new reports for Oregon State University web application using SSRS and T-SQL stored procedures to allow users to see data from database in an organized and clean fashion.
 \end{itemize}
\end{resume}
\end{document}
